Time delay estimation in non-resolved lensed quasars

### 2020-11-23 paper/aa-package/paper.tex
improve abstract

  \abstract
  % context heading (optional)
  % {} leave it empty if necessary  
   {
   	The analysis of Cosmic Microwave Background anisotropies and the cosmic distance ladder observations have resulted in a tension on the estimated value of the Hubble parameter $H_0$. This has triggered the need for new methods for its determination. To this extent, the H0LiCoW collaboration has reported a $2.4\%$ measurement of $H_0$ based on time delay measurements of six gravitational lensed quasars. Such value is compatible with the distance ladder observations, increasing the tension at the $5.3 \sigma$ level.
   	}
  % aims heading (mandatory)
   { 
   	The fractional error on $H_0$, obtained with the gravitational lensing method, decreases linearly with the number of lensed systems analysed. Moreover, such method is highly affected by the microlensing phenomenon, which can produce changes in the actual time delay of the order of days. To account for these two facts, more lensed systems should be analysed and, possibly, with a regular and long-term monitoring of the lensed source, of the order of years. This cannot be achieved with big telescopes, due to the huge amount of observational requests they have to fulfill. On the other hand, small/medium-sized telescopes are present in a much larger number and are often characterized by more versatile observational programs. However, the limited resolution capabilities of such instruments and their often not privileged geographical location prevent them from providing well-separated images of the same lensed source. 
   	\\
   	In this work, we present a novel approach to estimate the time-delay in unresolved lensed quasar systems. Our method is further motivated by recent developments in discovering more unresolved strongly-lensed QSO systems.
	}
  % methods heading (mandatory)
   {Our method uses ...}
  % results heading (mandatory)
   {...}
  % conclusions heading (optional), leave it empty if necessary 
   {}

>>>>

  \abstract
  % context heading (optional)
  % {} leave it empty if necessary  
   {
   	Early universe (EU) measurements and late universe (LU) observations have resulted in a tension on the estimated value of the Hubble parameter $H_0$. Time-delay cosmography offers an alternative method to measure $H_0$. In this context, the H0LiCoW collaboration has reported a $2.4\%$ measurement of $H_0$ compatible with LU observations, increasing the tension at the $5.3 \sigma$ level. Whereas, TDCOSMO+SLACS has reported a $5\%$ measurement of $H_0$ in agreement with both EU and LU estimates, showing the need to collect more data in order to reduce the error in the $H_0$ estimation.
   	}
  % aims heading (mandatory)
   { 
   	The fractional error on $H_0$, obtained with time-delay cosmography, decreases linearly with the number of lensed systems analysed. Moreover, such method is highly affected by the microlensing phenomenon, which can produce changes in the actual time delay of the order of days. To account for these two facts, more lensed systems should be analysed and, possibly, with a regular and long-term monitoring of the lensed source, of the order of years. This cannot be achieved with big telescopes, due to the huge amount of observational requests they have to fulfill. On the other hand, small/medium-sized telescopes are present in a much larger number and are often characterized by more versatile observational programs. However, the limited resolution capabilities of such instruments and their often not privileged geographical location prevent them from providing well-separated images of the same lensed source. 
   	\\
   	In this work, we present a novel approach to estimate the time-delay in unresolved lensed quasar systems. Our method is further motivated by recent developments in discovering more unresolved strongly-lensed QSO systems.
	}
  % methods heading (mandatory)
   {Our method uses ...}
  % results heading (mandatory)
   {...}
  % conclusions heading (optional), leave it empty if necessary 
   {}
